Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-02 paper.tex
Reduction of text in introduction. Some errors fixed. Classification term changed by regression

Despite the fact that errors in one or the other direction do not have
the same impact, it is extremely important to develop an accurate
predictive method 
which could forecast the future sales a new book will achieve, in
order to optimise production schedules, improve the publishing company
profits and minimise losses \cite{Zhao2001}, being the latter the main
objective of this paper.  This is the main problem we are going to
tackle in this paper.

@@

Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a  company that sells
software for publishers, we analyse it by means of different data
mining methods and create predictive models that can be mainly used as
decision-aid tools for book publishers. With these models, publishers
will be able to 
combine their expert knowledge about the market with the created
forecasting models in order to get a reliable estimation of book
sales, and, based on it, act upon it to maximize the books sold for a
particular print run. Our main contribution is, thus, to develop a
methodology to process book sales data in order to first find out
relevant variables and then use these variables to process data so
that the publisher, using them, can estimate sales and from them order
a specific print run, instead of standard ones, which are around 300
copies for standard books and around 5000 for those that are
considered, in advance, {\em best sellers}.

In the research published in this paper, the problem 
of predicting total sales in order to print the right amount of books
%of how many units should be printed  when a new book is published 
is approached using real data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data
and applied their knowledge on external variables to compute correct
estimations (predictions); for instance, they can decide increasing or
decreasing the sales forecast based on season or sales period. 
Nevertheless, just carrying out the analysis and forecasting process
as a human expert may lead to imprecise predictions, and they may not
take all the variables into account.  
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function: Euclidean, Minkowsky or minimax.

@@

In classification problems the algorithm searches for an optimal hyperplane 
that separates two classes, maximising the margin between them. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples, 
called support vectors.
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation problems.

@@

The aim of these algorithms is exploring the space of attributes to find out 
which subset of them yields the best results in a classification or prediction 
problem. To this end, the features describing every pattern are analysed. 
In this case, among the variables describing a new book, some may affect 
predictions as they provide information, while others may not be necessary 
and even redundant.

@@

As far as the different methods are concerned, M5P model obtained the best results, both in time and error. The advantage of M5P is that it can learn and tackle classification tasks that have high dimensionality and categorical variables efficiently. Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation. Thus, it is a very suitable model be incorporated in a publishing company 
processes (as we will show in Section \ref{subsec:decision_trees}).

@@

The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset. First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (RFE, CSE and SOM) are used to reduce the set of features in each case. Second, the classification models are applied again on the reduced datasets to evaluate their performance.

@@

\begin{table*}
\caption{Predicting Total sales for publishing company-UDL929 (The best selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
\hline 
kNN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
MLP	& 84.42 $\pm$ 0.12	& 1105.61 $\pm$ 445.66	& 1776.68 $\pm$ 1148.31	& 66.52 $\pm$ 23.63	& 70.41 $\pm$ 41.88	& 1.65 $\pm$ 0.008 \tabularnewline
\hline
\end{tabular}
}
\label{Table:case1results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo-UDLW12 (The median selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
\hline 
RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
\hline 
MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
\hline
\end{tabular}
}
\label{Table:case2results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo704 (highest number of different titles sold). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
\hline 
kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
\hline
\end{tabular}
}
\label{Table:case3results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for PublishingCo-UDLU11 (medium number of different books sold)). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
\hline 
RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
MLP	& 0.7649 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
\hline
\end{tabular}
}
\label{Table:case4results}
\end{table*}

@@

In this stage of the experiments for the special cases, the
feature selection methods (RFE, CSE and SOM) are applied for each case
independently, since publishers with different sales ranges, and
targets, might in fact include different factors or have different
leverage when deciding how much to print. For clarity purpose, we present 
here only the results after applying the RFE method for the four cases in Tables
\ref{Table:case1results-RAE}, \ref{Table:case2results-RAE},
\ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}, this
one was chosen since the selected features by this
method showed in the previous experiment the highest predictive power among 
all classifiers. 
%According to the aforementioned tables, 
%It's not according to a table. It's according to the results there - JJ
RFE reduction has noticeably improved the performance of all classifiers 
specially in the case of the best selling publisher house (i.e. UDL929) and the
publisher which publishes a wide range of different books (i.e. UDL704). 
For the rest of the results which are obtained by CSE and SOM feature selection 
methods we refer the reader to the appendix of tables at the end of this paper.

\begin{table*}[!ht]
% Why the capital in Total? If it's a variable use Small Caps or Sans
% Serif - JJ
\caption{Predicting Total sales for PublishingCo-UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
\hline 
kNN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
\hline 
LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
\hline 
MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
\hline
\end{tabular}
}
\label{Table:case1results-RAE}
\end{table*}

\begin{table*}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
\hline 
kNN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
\hline 
RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
\hline 
LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
\hline 
MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case2results-RAE}
\end{table*}

>>>>

Despite the fact that errors in one or the other direction do not have
the same impact, it is extremely important to develop an accurate
predictive method 
which could forecast the future sales a new book will achieve, in
order to optimise production schedules, improve the publishing company
profits and minimise losses \cite{Zhao2001}. This is the main objective of this paper.

@@

Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a  company that sells
software for publishers, we analyse them and compute predictive models that can be mainly used as decision-aid tools for book publishers. With these models, publishers will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book
sales, and, based on it, act consequently in order to maximize the books sold for a particular print run. This will improve the current decision flow that the publishers follow, which consist in analysing (in a subjective way) the quality of the book and its features (author, genre, etc), and take a `fuzzy' decision roughly between printing 300 copies (standard book) or 5000 (best seller).

Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out
relevant variables, and then, use these variables to process the data to accurately estimate future sales.

In the research published in this paper, the problem of predicting total sales is approached using real data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. This company offers management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data
and applied their knowledge on external variables to compute correct
estimations (predictions); for instance, they can decide increasing or
decreasing the sales forecast based on season or sales period. 
Nevertheless, just carrying out the analysis and forecasting process
as a human expert may lead to imprecise predictions, and they may not
take all the variables into account.  
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
% Antonio - should we change the term 'classification' by 'regression' somehow?

@@

%In classification problems the algorithm searches for an optimal hyperplane 
%that separates two classes, maximising the margin between them.
% Antonio - remove this classification thing due to a reviewer's comment 
In regression problems, the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples, 
called support vectors.
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation problems.
% Antonio - something about regression?

@@

The aim of these algorithms is exploring the space of attributes to find out 
which subset of them yields the best results in a regression or prediction 
problem. To this end, the features describing every pattern are analysed. 
In this case, among the variables describing a new book, some may affect 
predictions as they provide information, while others may not be necessary 
and even redundant.

@@

As far as the different methods are concerned, M5P model obtained the best results, both in time and error. The advantage of M5P is that it can learn and tackle regression
% Antonio - I think we can change classification by regression. I have done. Check it out. ;)
 tasks that have high dimensionality and categorical variables efficiently. Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation. Thus, it is a very suitable model be incorporated in a publishing company 
processes (as we will show in Section \ref{subsec:decision_trees}).

@@

The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset. First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (RFE, CSE and SOM) are used to reduce the set of features in each case. Second, the regression models are applied again on the reduced datasets to evaluate their performance.

@@

\begin{table*}
\caption{Predicting Total sales for publishing company UDL929 (The best selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{90.0 $\pm$0.10} &  \textbf{670.24 $\pm$181.05}  &  \textbf{1065.34 $\pm$413.84}  &  \textbf{40.83 $\pm$10.86}  &  \textbf{43.56 $\pm$19.87}  & 0.03 $\pm$0.002\tabularnewline
\hline 
kNN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  &  \textbf{0 $\pm$0.0001}\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
MLP	& 84.42 $\pm$ 0.12	& 1105.61 $\pm$ 445.66	& 1776.68 $\pm$ 1148.31	& 66.52 $\pm$ 23.63	& 70.41 $\pm$ 41.88	& 1.65 $\pm$ 0.008 \tabularnewline
\hline
\end{tabular}
}
\label{Table:case1results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for publishing company UDLW12 (The median selling publishing company). Best values in bold. }
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
kNN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  &  \textbf{0.0001 $\pm$0.0002}\tabularnewline
\hline 
RF &  \textbf{85.8 $\pm$0.17}  & 14.19 $\pm$6.69  &  \textbf{23.57 $\pm$11.83}  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  &  \textbf{14.01 $\pm$7.61}  & 25.61 $\pm$15.30  &  \textbf{40.66 $\pm$16.03}  &  \textbf{53.28 $\pm$18.45}  & 0.02 $\pm$0.02\tabularnewline
\hline 
MLP	& 71.33 $\pm$ 0.35	& 27.46 $\pm$ 14.59	& 49 $\pm$ 34.83	& 82.5 $\pm$ 38.48	& 108.85 $\pm$ 66.21	& 0.45 $\pm$ 0.004\tabularnewline
\hline
\end{tabular}
}
\label{Table:case2results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for publishing company UDL704 (highest number of different titles sold). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  &  \textbf{88.9 $\pm$0.07} &  \textbf{71.26 $\pm$21.29}  &  \textbf{125.19 $\pm$50.09}  &  \textbf{39.25 $\pm$11.77}  &  \textbf{47.50 $\pm$15.93}  & 0.05 $\pm$0.03\tabularnewline
\hline 
kNN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
MLP	& 80.83 $\pm$ 0.12	& 122.8 $\pm$ 56.86	& 207.12 $\pm$ 100.44	& 67.13 $\pm$ 31.38	& 78.14 $\pm$ 39.92	& 2.83 $\pm$ 0.012\tabularnewline
\hline
\end{tabular}
}
\label{Table:case3results}
\end{table*}

\begin{table*}
\caption{Predicting Total sales for publishing company UDLU11 (medium number of different books sold)). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
kNN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  &  \textbf{0 $\pm$0.0002}\tabularnewline
\hline 
RF &  \textbf{86.7 $\pm$0.07}  &  \textbf{449.16 $\pm$127.80}  &  \textbf{671.76 $\pm$212.74}  &  \textbf{45.58 $\pm$9.80}  &  \textbf{51.37 $\pm$11.16}  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
MLP	& 0.7649 $\pm$ 0.17	& 757.12 $\pm$ 270.14	& 1111.03 $\pm$ 645.27	& 78.74 $\pm$ 31.38	& 88.05 $\pm$ 54.96	& 1.11 $\pm$ 0.004\tabularnewline
\hline
\end{tabular}
}
\label{Table:case4results}
\end{table*}

@@

In this stage of the experiments for the special cases, the
feature selection methods (RFE, CSE and SOM) are applied for each case
independently, since publishers with different sales ranges, and
targets, might in fact include different factors or have different
leverage when deciding how much to print. For clarity purpose, we present 
here only the results after applying the RFE method for the four cases in Tables
\ref{Table:case1results-RAE}, \ref{Table:case2results-RAE},
\ref{Table:case3results-RAE} and \ref{Table:case4results-RAE}, this
one was chosen since the selected features by this
method showed in the previous experiment the highest predictive power among 
all classifiers. 
% Antonio - could we use any sinonym of classifier but for regression... I guess 'regressor' is not appropriate. :D
%
%According to the aforementioned tables, 
%It's not according to a table. It's according to the results there - JJ
RFE reduction has noticeably improved the performance of all classifiers 
specially in the case of the best selling publisher house (i.e. UDL929) and the
publisher which publishes a wide range of different books (i.e. UDL704). 
For the rest of the results which are obtained by CSE and SOM feature selection 
methods we refer the reader to the appendix of tables at the end of this paper.

\begin{table*}[!ht]
% Why the capital in Total? If it's a variable use Small Caps or Sans
% Serif - JJ
\caption{Predicting Total sales for publishing company UDL929 (ReliefFAttributeEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P &  \textbf{90.5 $\pm$0.1} &  \textbf{661.81 $\pm$186.17} &  \textbf{1070.24 $\pm$425.66} &  \textbf{40.18 $\pm$10.50} &  \textbf{43.56 $\pm$19.77} & 0.02 $\pm$0.002\tabularnewline
\hline 
kNN & 87.8 $\pm$0.11 & 751.54 $\pm$270.91 & 1257.82 $\pm$615.66& 44.57 $\pm$10.89 & 48.62 $\pm$18.73 &  \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 88.3 $\pm$0.11 & 735.04 $\pm$326.9 & 1420.43 $\pm$941.62 & 43.56 $\pm$15.88 & 54.36 $\pm$35.31 & 0.10 $\pm$0.009\tabularnewline
\hline 
LR & 88.4 $\pm$0.11 & 868.18 $\pm$208.65 & 1231.23 $\pm$454.86 & 53.38 $\pm$14.67 & 50.60 $\pm$22.04 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.6 $\pm$0.10 & 860.49 $\pm$334.67 & 1560.05 $\pm$962.64 & 49.98 $\pm$9.68 & 55.07 $\pm$17.76 & 0.023 $\pm$0.003\tabularnewline
\hline 
MLP	& 87.66 $\pm$ 0.14	& 897.02 $\pm$ 411.58	& 1332.54 $\pm$ 969.05	& 56.43 $\pm$ 33.1	& 58.52 $\pm$ 57.68	& 0.17 $\pm$ 0.002\tabularnewline
\hline
\end{tabular}
}
\label{Table:case1results-RAE}
\end{table*}

\begin{table*}[!ht]
\caption{Predicting Total sales for publishing company UDLW12 (ReliefFAttributeEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 83.7 $\pm$0.24 & 13.85 $\pm$6.56 & 23.19 $\pm$11.80 & 42.35 $\pm$20.33 & 54.08 $\pm$30.06 & 0.0063 $\pm$0.0014\tabularnewline
\hline 
kNN & 77.2 $\pm$0.30 & 14.18 $\pm$6.63 & 23.65 $\pm$11.03 & 43.37 $\pm$19.23 & 57.00 $\pm$30.59 &  \textbf{0 $\pm$0.0001}\tabularnewline
\hline 
RF &  \textbf{86.7 $\pm$0.16} & 13.63 $\pm$6.67 & 22.80 $\pm$11.81 & 41.07 $\pm$17.71 & 52.43 $\pm$26.23 & 0.0304 $\pm$0.0025\tabularnewline
\hline 
LR & 84.4 $\pm$0.25 &  \textbf{12.79 $\pm$6.65} &  \textbf{21.52 $\pm$12.54} & 39.47 $\pm$23.35 &  \textbf{50.14 $\pm$35.26} & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 85.2 $\pm$0.19 & 13.22 $\pm$7.39 & 24.41 $\pm$15.09 &  \textbf{38.24 $\pm$15.41} & 50.46 $\pm$17.97 & 0.014 $\pm$0.002\tabularnewline
\hline 
MLP	& 79.26 $\pm$ 0.27	& 20.28 $\pm$ 13.25	& 35.05 $\pm$ 29.44	& 61.89 $\pm$ 37.64	& 81.51 $\pm$ 63.39	& 0.07 $\pm$ 0.002\tabularnewline
\hline 
\end{tabular}
}
\label{Table:case2results-RAE}
\end{table*}
